Points Above Replacement

### 2022-03-02 Code/PointGuardPAR.Rmd
Add files via upload

```{r methods, echo=FALSE}
offensivePoints<-function(effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
+ {(200*effectiveFieldGoalPercentage)+(300*threePointPercentage)+(100*freeThrowPercentage)+(offensiveRebounds)+(3*assists)+(2*points)-(5*turnovers)}
pgOffensivePoints <- mapply(offensivePoints, effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
defensivePoints <-function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
+ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(3*blocks)-(3*personalFouls)}
pgDefensivePoints<-mapply(defensivePoints, defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
offensiveAndDefensivePoints<-function(pgOffensivePoints, pgDefensivePoints)
+ {pgOffensivePoints+pgDefensivePoints}
pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
positionalAdjustment<-function(minutesPlayed, points, teamTotalPoints)
+ {(minutesPlayed/3456)*(points/teamTotalPoints)}
pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed, points, teamTotalPoints)
pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
+  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+72}
pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
PAR<-function(pgOffensiveAndDefensivePoints, pgPositionalAdjustment, pgPointsPerWin)
+ {(pgOffensiveAndDefensivePoints*pgPositionalAdjustment)/pgPointsPerWin}
pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgPositionalAdjustment,pgPointsPerWin)))
print('PAR Data')
print(pgPAR)
```

>>>>

```{r methods, echo=FALSE}
offensivePoints<-function(effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
+ {(200*effectiveFieldGoalPercentage)+(300*threePointPercentage)+(100*freeThrowPercentage)+(offensiveRebounds)+(3*assists)+(2*points)-(5*turnovers)}
pgOffensivePoints <- mapply(offensivePoints, effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
defensivePoints <-function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
+ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(3*blocks)-(3*personalFouls)}
pgDefensivePoints<-mapply(defensivePoints, defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
offensiveAndDefensivePoints<-function(pgOffensivePoints, pgDefensivePoints)
+ {pgOffensivePoints+pgDefensivePoints}
pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
teamAdjustment<-function(minutesPlayed, points, teamTotalPoints)
+ {(minutesPlayed/3456)*(points/teamTotalPoints)}
pgTeamAdjustment<-mapply(teamAdjustment, minutesPlayed, points, teamTotalPoints)
pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
+  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+72}
pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
PAR<-function(pgOffensiveAndDefensivePoints, pgTeamAdjustment, pgPointsPerWin)
+ {(pgOffensiveAndDefensivePoints*pgTeamAdjustment)/pgPointsPerWin}
pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgTeamAdjustment,pgPointsPerWin)))
print('PAR Data')
print(pgPAR)
```
